No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-17 main/LICS.tex
more minor edits

\begin{definition} 
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges, between vertices $v(e)=\{v_1,v_2\}\subseteq V$ and with \emph{weight} $w\colon E\to\mathbb N$.
%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

@@

A \emph{(partial) configuration} for an \textsc{ncg} is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

@@

\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

@@

\begin{IEEEproof}
Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
%
%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\sim\delta'$ or $\gamma'=\delta'$; secondly,
%
if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
%
\end{IEEEproof}

@@

\begin{definition}
\label{def:graph interpretation}
The \emph{interpretation} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.

The interpretation of a vertex $v_k$ is the formula
\[
	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
\]
where each \emph{constraint element} $C$ is the formula
\[
	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
\]

The interpretation of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W$ is the formula
\[
	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
\]

The interpretation of the graph $G$ is the sequent
\[
	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
\]
where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.

@@

\begin{definition}
\label{def:configuration interpretation}
The \emph{interpretation} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
%
Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
\end{definition}

@@

\begin{definition}
For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

>>>>

\begin{definition} 
A \emph{constraint graph} $G=(V,E,c,v,w)$ consists of: a set $V$ of vertices with \emph{inflow constraint} $c\colon V\to\mathbb N$; and a set $E$ of undirected edges with \emph{weight} $w\colon E\to\mathbb N$, connecting vertices $v(e)=\{v_1,v_2\}\subseteq V$.
%of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

@@

A \emph{(partial) configuration} for a constraint graph is a (partial) function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$, if $\gamma(e)$ is defined then $\gamma(e)\in v(e)$,
	\item
for every vertex $v$, the sum of its inflow weights is at least its inflow constraint, $\sum\{w(e)\mid \gamma(e)=v\}\geq c(v)$.
\end{itemize}

@@

\emph{Non-deterministic constraint graph reconfiguration} or \emph{\textsc{ncg}-reconfiguration} is the problem of deciding when two configurations for a constraint graph are connected in the graph of total configurations and reconfiguration steps.
%
\emph{Partial \textsc{ncg}-reconfiguration} is the same problem for partial configurations.

%\emph{(Partial) \textsc{ncg}-reconfiguration} is the problem of deciding when two (partial) configurations are connected by a path in the graph of (partial) configurations and reconfiguration steps.

@@

\begin{IEEEproof}
Partial \textsc{ncg}-reconfiguration simulates \textsc{ncg}-reconfiguration:
%
%There is a path between total configurations $\gamma$ and $\delta$ in partial \textsc{ncg}-reconfiguration if and only if there is one in \textsc{ncg}-reconfiguration, for the following two reasons.
%
firstly, if $\gamma\perm*\delta$ for partial configurations, then these may be completed to total configurations $\gamma'\perm*\delta'$ or $\gamma'=\delta'$; secondly,
%
if $\gamma'$ and $\gamma''$ are total configurations that both agree with a partial configuration $\gamma$ where it is defined, then $\gamma'$ and $\gamma''$ are connected in \textsc{ncg}-reconfiguration by reversing the edges on which they disagree.
%
\end{IEEEproof}

@@

\begin{definition}
\label{def:graph encoding}
The \emph{encoding} $\itn G$ of an \textsc{ncg} $G=(V,E,c,v,w)$ is a sequent constructed as follows.
%
Let $V=\{v_1,\dotsc,v_n\}$ and $E=\{e_1,\dotsc,e_m\}$ where $|V|=n$ and $|E|=m$.

The encoding of a vertex $v_k$ is the formula
\[
	\itn{v_k} = \bigparr\big(C^{m\times c(v_k)} \big)\parr 1
\]
where each \emph{constraint element} $C$ is the formula
\[
	C = \bigparr\big(1^{3k+2}\big) \tn \bigparr\big(1^{3(n-k)+3}\big)
\]

The encoding of an edge $e$ connecting vertices $v_i$ and $v_j$ with $i<j$ is the formula
\[
	\itn{e} = \bigotimes\big(W^{m\times w(e)}\big)\tn\bot
\]
where each \emph{weight element} $W$ is the formula
\[
	W = \bigotimes\big(\bot^{3i+2}\big)\parr\bigotimes\big(\bot^{3(j-i)+1}\big)\parr\bigotimes\big(\bot^{3(n-j)+3}\big)
\]

The encoding of the graph $G$ is the sequent
\[
	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_m}, 1^p
\]
where $p=m\times(|w|-|c|)\times(3n+4)$; the $p$ instances of $1$ are called \emph{edge-absorbers}.

@@

\begin{definition}
\label{def:configuration encoding}
The \emph{encoding} $\itn\gamma$ of a total configuration $\gamma$ for a graph $G$ is a linking $\links$ constructed incrementally, for each successive edge $e$, and for each successive weight element $W$ within $e$, as follows.
%
Let $\gamma(e)=v$; firstly, the the indicator vertex of $\itn e$ links to the indicator of $\itn v$.
%
Then successively for each weight element $W$ in $e$, if $\itn v$ has a first free constraint element $C$, extend $\itn\gamma$ to include the natural linking on $W,C$; otherwise, extend $\itn\gamma$ by the natural linking on the sequent consisting of $W$ plus the first $3n+4$ free edge absorbers.
\end{definition}

@@

\begin{definition}
For a proof net $\links$ for $\itn G$, let $\coitn\links$ be the partial configuration for $G$ where $\coitn\links(e)$ is $v$ if 1) $e$ is appropriate for $v$ and 2) $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}
